---
title: "Sentiment analysis of tweets directed at @Apple Before and After its Quarterly results announcement."
output: html_notebook
---

#### Importing the tweet data directed at Apple before its quarterly results from CSV file and building a Corpus of that
```{r}
# Importing text mining (tm) library
library(tm)

# Read file
apple_tweets <- read.csv('apple_pre_earnings.csv', header=T)

# Changing character encoding of data in text column to UTF-8
apple_tweets_utf8 <- iconv(apple_tweets$text, to = 'utf-8')

# Converting the data into Corpus format
apple_corpus <- Corpus(VectorSource(apple_tweets_utf8))

# View the content of the 1st 5 documents in the corpus
inspect(apple_corpus[1:5])
```

#### Cleaning the data
```{r}
# Converting all text to lower case
apple_corpus <- tm_map(apple_corpus, tolower)
inspect(apple_corpus[1:5])

# Removing all punctuations
apple_corpus <- tm_map(apple_corpus, removePunctuation)
inspect(apple_corpus[1:5])

# Removing all numbers
apple_corpus <- tm_map(apple_corpus, removeNumbers)
inspect(apple_corpus[1:5])

# Removing most-commonly used English words as they don't provide any value
cleanset <- tm_map(apple_corpus, removeWords, stopwords('english'))
inspect(cleanset[1:5])

# Removing URL's
removeURL <- function(x) gsub('http[[:alnum:]]*', '', x)
cleanset <- tm_map(cleanset, content_transformer(removeURL))
inspect(cleanset[1:5])

# Removing aapl and apple as they would appear very frequently but provide little value
cleanset <- tm_map(cleanset, removeWords, c('aapl', 'apple'))
inspect(cleanset[1:5])

# Replacing stocks with stock so they don't get double counted
cleanset <- tm_map(cleanset, gsub, pattern='stocks', replacement='stock')

# Strip whitespaces
cleanset <- tm_map(cleanset, stripWhitespace)
inspect(cleanset[1:5])
```
#### Using Term-Document Matrix (TDM) data structure to find patterns and extract info.\ 
#### It helps us convert the unstructured data into structured rows and columns.
```{r}
# Converting cleanset into a TDM data structure
tdm <- TermDocumentMatrix(cleanset)
tdm
# Converting TDM to matrix
tdm <- as.matrix(tdm)
# Display the first 10 words from 20 columns
tdm[1:10, 1:20]
```

#### Plotting a bar plot
```{r}
# Finding rowsum i.e. frequency count for each word
w <- rowSums(tdm)

# Filtering out words that have frequency less than 25
w <- subset(w, w>=25)

# Plotting the barplot 
barplot(w, las=2, col = rainbow(50))
```

#### Creating a wordcloud out of our data
```{r}
library(wordcloud)
w <- sort(rowSums(tdm), decreasing=TRUE)
set.seed(222)
wordcloud(
  words=names(w), 
  freq = w, 
  max.words=150, 
  random.order=FALSE, 
  colors=brewer.pal(8, 'Dark2'), 
  scale=c(5, 0.3), 
  rot.per=0.3)
```

### Performing Sentiment analysis for tweets directed at @Apple BEFORE it announced its Quarterly earnings
```{r}
library(syuzhet)
library(lubridate)
library(ggplot2)
library(scales)
library(reshape2)
library(dplyr)

# Read file
apl_tweets <- read.csv('apple_pre_earnings.csv', header=T)
apl_tweets_utf8 <- iconv(apl_tweets$text, to='utf-8')

# Obtaining sentiment scores
sentiments <- get_nrc_sentiment(apl_tweets_utf8)
sentiments
```

#### Plotting barplot for every tweets sentiments BEFORE it announced its Quarterly earnings
```{r}
barplot(colSums(sentiments),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores of Tweets directed at Apple BEFORE its quarterly earnings')
```

### Performing Sentiment analysis for tweets directed at @Apple AFTER it announced its Quarterly earnings
```{r}
# Read file
apl_post_tweets <- read.csv('apple_post_earnings.csv', header=T)
apl_post_tweets_utf8 <- iconv(apl_post_tweets$text, to='utf-8')

# Obtaining sentiment scores
sentiments_post <- get_nrc_sentiment(apl_post_tweets_utf8)
sentiments_post
```

#### Plotting barplot for every tweets sentiments AFTER it announced its Quarterly earnings
```{r}
barplot(colSums(sentiments_post),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores of Tweets directed at Apple AFTER its quarterly earnings')
```

## <u>Conclusion</u>: Thus, we see that after Apple published its Quartlerly earnings, there is a decrease in negative emotions and increase in positive emotions.